---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
## Overview
'"binomial"' is an R pacakge that implements functions for calculating probabilities of a binomial random variable, and related calcualtions such as the probability distribution, the expected value, variance, etc.

## Motivation 
This package had been developed to help the author gain familiarity with building R packages and provide tools for calculating probabilties of binomial random variables.

## Installation

You can install the released version of binomial from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("binomial")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("stat133-sp19/hw-stat133-elainekwan")
```
## Usage

```{r example}
library(binomial)
## basic example code

# probability of getting 2 successes in 5 trials
# (assuming prob of success = 0.5)
bin_probability(success = 2, trials = 5, prob = 0.5)

# binomial probability distribution
bin_distribution(trials = 5, prob = 0.5)

# plotting binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
plot(dis1)

# binomial cumulative distribution
bin_cumulative(trials = 5, prob = 0.5)

# plotting binomial cumulative distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
plot(dis2)

# summary of a binomial variable
bin1 <- bin_variable(trials = 10, p = 0.3)
binsum1 <- summary(bin1)
binsum1

# functions of measures
bin_variance(10, 0.3)
bin_mode(10, 0.3)
bin_skewness(10, 0.3)
bin_kurtosis(10, 0.3)
```
